Pillar 2 - Topic Modeling

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
LDA on description, overview and manual

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
    fig_heigt: 8
    fig_width: 16
---

@@

rm(compute_tf_idf())
```

@@

## Cluster Level
```{r tf-idf per cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

## Concentration Level
```{r, cache = TRUE}
prepare_tf_idf_concentration <- function(data) data %>%
                                                 left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                                 filter(!is.na(Concentration)) %>%
                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                                 rename(facet = Concentration) %>%
                                                 group_by(facet, word) %>%
                                                   summarise(tf_idf = sum(tf_idf),
                                                             n = sum(n)) %>%
                                                   filter(n >= 10) %>%
                                                   top_n(10, tf_idf) %>%
                                                 ungroup

@@

# LDA
## Fitting Model
```{r, eval = FALSE}
d_overview_cast <- d_overview %>%
  count(Code, word, sort = T) %>%
  cast_dtm(Code,word, n)
```

```{r, eval = FALSE}
LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))
LDA_17 <- LDA(d_overview, k = 17, control = list(seed = 123))
LDA_25 <- LDA(d_overview, k = 25, control = list(seed = 123))
```

>>>>

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

rm(compute_tf_idf)
```

@@

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data) data %>%
                                                 left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                                 filter(!is.na(Concentration)) %>%
                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                                 rename(facet = Concentration) %>%
                                                 group_by(facet, word) %>%
                                                   summarise(tf_idf = sum(tf_idf),
                                                             n = sum(n)) %>%
                                                   filter(n >= 10) %>%
                                                   top_n(10, tf_idf) %>%
                                                 ungroup

@@

# LDA
## Fitting Model
```{r}
my_cast_tdm <- function(data, level) data %>%
  count(Code, word) %>%
  cast_dtm(Code, word, n)

d_description_cast <- my_cast_tdm(d_description)
d_overview_cast <- my_cast_tdm(d_overview)
d_manual_cast <- my_cast_tdm(d_manual)
```

```{r, eval = FALSE}
LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))

LDA_overview_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
LDA_overview_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
LDA_overview_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))

LDA_manual_10 <- LDA(d_manual_cast, k = 10, control = list(seed = 123))
LDA_manual_17 <- LDA(d_manual_cast, k = 17, control = list(seed = 123))
LDA_manual_25 <- LDA(d_manual_cast, k = 25, control = list(seed = 123))
```
